curling

### 2020-07-29 inst/curling.Rmd
fixes  #58

```{r,definsupportb}
H1 <- ordertable2supp(ct)
head(H1)
(mH1 <- maxp(H1))
pie(mH1)
```

@@

```{r,plotcomplog}
par(pty="s")
plot(log10(mH1),log10(mH2),asp=1,pch=16,xlim=c(-2.6,0),ylim=c(-2.6,0))
posn <- c(Canada=1, China=2, Denmark=4, Germany=4, GB=4, Italy=1, Japan=4, Norway=4,
          Russia=2, South_Korea=4, Sweden=2, Switzerland=2, US=4)
for(i in seq_len(nrow(curling_table))){
	text(log10(mH1)[i],log10(mH2)[i],rownames(curling_table)[i],col="gray",pos=posn[i])
}
abline(0,1)
grid()
```

Note that the two strongest competitors, Canada and Sweden, switch
between first and second in the two systems.

>>>>

```{r,definsupportb,cache=TRUE}
H1 <- ordertable2supp(ranktable_to_ordertable(wikitable_to_ranktable(ct)))
H1
mH1 <- maxp(H1)
pie(mH1)
```

@@

```{r,plotcomplog}
par(pty="s")
plot(log10(mH1),log10(mH2),asp=1,pch=16,xlim=c(-2.6,0),ylim=c(-2.6,0))
posn <- c(Canada=2, China=4, Denmark=4, Germany=4, GB=4, Italy=1, Japan=2, Norway=2,
          Russia=4, South_Korea=4, Sweden=4, Switzerland=2, US=4)
for(i in seq_len(nrow(curling_table))){
	text(log10(mH1)[i],log10(mH2)[i],rownames(curling_table)[i],col="gray",pos=posn[i])
}
abline(0,1)
grid()
```

The two likelihood systems have very different evaluates.
